Well Hello There!

### 2023-11-23 about.qmd
Project Update

---
title: "Data Story"
---

<br>

### Investigating Singapore's Resale Flat Prices from 1990 to 2023

##### Is public housing in Singapore affordable for the average Singaporean?

<br> This is where my introduction will be. This is just a placeholder for potential data sets!

```{r, eval=TRUE,echo=FALSE}
library(tidyverse)
starwars
```

>>>>

---
title: "My Experiences"
---

![](src/images/aboutme.png)

## My Work and Internship Experience - [My LinkedIn Profile](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)

**- Specialist**\
*Apple South Asia* <br> Aug 2023 - Present · 4 mos

**- Galaxy Specialist · Part-time**\
*Samsung Electronics Singapore* <br>Feb 2018 - Jan 2023 · 5 yrs

**- Business Information Technology Interest Group - Honorary Secretary**\
*Temasek Polytechnic* <br>Apr 2019 - Apr 2021 · 2 yrs 1 mo

**- Application Development Intern**\
*Accenture · Internship* <br>Apr 2020 - Aug 2020 · 5 mos

**- Marketing Research Intern**\
*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos

**- Instructor**\
*Singapore Civil Defence Force · Full-time* <br>Feb 2016 - Nov 2017 · 1 yr 10 mos

**- Attraction Host Lead**\
*Sentosa Development Corporation · Part-time* <br>Oct 2013 - Nov 2015 · 2 yrs 2 mos

### 2023-11-23 index.qmd
update
Project Update

---
title: "Marzuki Nooranas"
---

@@

### [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}

library(grid)
library(gridExtra)
library(png)

img1 <- readPNG("src/images/me_icon.png")
img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")

grid.arrange(rasterGrob(img1, width=unit(1.1,"npc"), height=unit(0.8,"npc"), gp=gpar(mai=c(0,0,0,0))), 
             rasterGrob(img2, width=unit(1,"npc"), height=unit(0.7,"npc"), gp=gpar(mai=c(0,0,0,0))), 
             ncol=2)

@@

@@

@@

#

>>>>

---
title: "Well Hello There!"
---

@@

![](src/images/namelogo.png){fig-align="left" width="724"}

@@

![](src/images/me2.jpg)

@@

### SC3101 - Social Thought and Theory

In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim. This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.

This idea that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today. How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!

{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}

### HS1501 - Artificial Intelligence and Society

In this module, we looked at the benefits and potential downsides of relying on AI. My group focused on leveraging on AI technology to aid in bereavement process. I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with thier loved ones - as an avatar!

![](docs/src/images/brochure.png)

@@
